### 2016-11-15 R/ITHIM.Rmd
Tweak to methods paper figure.

p <- ggplot(DTotal, aes(x = at,y = -DALYs/1e3))#, colour = quants))
p + stat_smooth( method = loess) + geom_point() + theme_bw() + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + scale_x_continuous(name="Active Transport (minutes/week) (Referent Group)") + facet_grid( . ~ muNonTravel) + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8))

>>>>

p <- ggplot(DTotal, aes(x = at, y = -DALYs/1e3, colour = muNonTravel), colour = muNonTravel)
p + geom_line() + geom_point() + theme_bw() + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + scale_x_continuous(name="Active Transport (minutes/week) (Referent Group)") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8)) #+ facet_grid( . ~ muNonTravel)

#p + stat_smooth( method = loess) + geom_point() + theme_bw() + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + scale_x_continuous(name="Active Transport (minutes/week) (Referent Group)") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8)) #+ facet_grid( . ~ muNonTravel)
